---
title: "Baltimore Religious Buildings"
author: "Nana-Ama"
date: "May 6, 2017"
output: html_document
---
##Injesting Baltimore City Data: Baltimore Religious Buildings


This project studies Baltimore City data provided by its local government on www.data.baltimorecity.gov. The purpose of this assignment is to learn how to import a chosen data set and plot its data. The data set I have chosen is the record of Baltimore's religious buildings. Using R packages, ggplot2 and ggmap, I am able to plot the buildings on a map of Baltimore. The map is map in order to see the spread of all 513 buildings throughout the entire city.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data }
source ("C:/Users/Tess/Downloads/Homework-2/RL.R")
#Religious_Buildings <-read_csv("C:/Users/Tess/Downloads/Religious_Buildings.csv)
#View(Religious_Buildings)
#This is the code in the sourced R script sourced file.  
library(readr)
library (knitr)
head (Religious_Buildings)
```

The code chunk above identifies the Religious Buildings data set. It also heads the first six lines and identifies the variables within it.

##Creating a map of Baltimore's Religious Buildings

```{r Baltimore, echo=FALSE}
library(ggmap)
library (ggplot2)
df <-geocode(Religious_Buildings$`Location 1`)
```

```{r gcode}
#library (ggmap)
#library(ggplot2)
#df <-geocode(Religious_Buildings$`Location 1`): code to pull coordinates
```
In order to create a map of the buildings using ggmap and ggplot2, the geographic coordinates of the various locations are required. This code creates a data frame of the coordinates to be plotted on top of a map of Baltimore which is generated all through ggmap.
```{r map, echo=FALSE}
ggplot(aes(x=lon, y=lat), data=df)
geocode("Baltimore")
qmplot(lon, lat, data = df,colour = I('red'), size = I(1), darken = .3)
```

##Fig.1 Baltimore City Religious Buildings
















This code chunk uses the properties of ggmap and ggplot2 to find the coordinates of Baltimore, create a coordinate map and plot the points on a map of Baltimore. There are 513 religious buildings in the city of Baltimore and on this graph.