---
title: "Baltimore Religious Buildings"
author: "Nana-Ama"
date: "May 6, 2017"
output: html_document
---
##Injesting Baltimore City Data: Baltimore Religious Buildings


This project studies Baltimore City data provided by its local government on www.data.baltimorecity.gov. The purpose of this assignment is to learn how to import a chosen data set and plot its data. The data set I have chosen is the record of Baltimore's religious buildings. Using R packages, ggplot2 and ggmap, I am able to plot the buildings on a map of Baltimore. The map is map in order to see the spread of all 513 buildings throughout the entire city.

```{r churches}
library(readr)
library(knitr)
source('~/Homework-2/readydata.R')
head (Religious_Buildings)
```
The code chunk above identifies the Religious Buildings dataset. It also heads the first six lines and identifies the variables within it.

##Creating the map of Baltimore Religious Buildings
```{r Baltimore}
library(ggmap)
library (ggplot2)
df <-geocode(Religious_Buildings$`Location 1`)
```
In order to create a map of the buildings using ggmap and ggplot2, the geographic coordinates of the various locations are required. This code creates a data frame of the coordinates to be plotted on top of a map of Baltimore which is generated all through ggmap.
```{r map}
geocode("Baltimore")
ggplot(aes(x=lon, y=lat), data=df)
qmplot(lon, lat, data = df,colour = I('red'), size = I(1), darken = .3)
```


##Fig.1 Baltimore City Religious Buildings


This code chunk uses the properties of ggmap and ggplot2 to find the coordinates of Baltimore, create a coordinate map and plot the points on a map of Baltimore.This map is the city layout of the religious  in Baltimore. 

 
